---
title: "CT COVID Map: Variations"
author: David Braze

output: 
  flexdashboard::flex_dashboard:
    theme: yeti
    orientation: columns
    vertical_layout: fill
---

```{css echo=FALSE}

h3  {
	font-size: 100px;
}

```

```{r setup, include=FALSE}

library(flexdashboard)
library(ggplot2)
library(FDBpub)

theme_set(FDBpub::theme_fdbplot(base_size=10))

theme_update(axis.line = element_blank(),
             axis.text = element_blank(),
             axis.ticks = element_blank(),
             panel.grid = element_blank(),
             panel.border = element_blank())

knitr::opts_chunk$set(fig.width=7,
                      fig.height=7/(16/9),
                      fig.align = "center", ## horz center figs on page
                      out.width="95%",
                      out.height="95%", 
                      dpi=if(doc_type()=="pdf") 300 else 200,
                      dev=if(doc_type()=="pdf") "cairo_pdf" else "png", 
                      dev.args=if(doc_type()=="pdf") NULL else list(type="cairo-png"),
                      echo=FALSE,
                      message=FALSE,
                      warning=FALSE,
                      include=TRUE,
                      results='asis',
                      cache=FALSE,
                      cache.lazy=FALSE)

```

```{r workhorse, include=FALSE}

source(here::here("ct-covid-map.R"))

```

# Intro

Choropleth maps are a way to show the geographic distribution of a statistic of interest (e.g., population density, household income) using color or shading. These maps provide an easy way to visualize how a variable differs across geographic areas, like states, counties, or towns.

In the tabs that follow, I've built three versions of choropleth maps depicting the 10 day average Covid-19 test postivity rate for Connecticut's 169 towns. The first is a static map built using basic functions from the {ggplot2} package. The next two are interactive maps. You can hover the mouse over each town for more detail. One was built using the ***R*** package {plotly}, the other with the {leaflet} package. Both of these rely on external javascript tools to do the actual work.

This data sketch is about choropleths as a data visualization method. It is not about Covid-19, as such. Those data were chosen just because they make a handy example. 

# GGplot

## Column {data-width=750}

### **GGplot**
	
```{r ggplot}

map.positivity

```

## Column {data-width=250}

### **Notes** 

This is a non-interactive map built with basic ggplot2 functions. 

I am using a shapefile-based set of multipolygons for the town outlines. 

On the following tabs, I've created interactive versions of this same figure using plotly::plot_ly() and leaflet::leaflet().

# Plot_ly

## Column {data-width=750}
 
### **Plot_ly** 

```{r plotly}

map.positivity.plotly

```

## Column {data-width=250}

### **Notes**

Interactive choropleth with plotly::plot_ly(). 

I'm using  a geojson-based set of polygons for town outlines in this map. Plot_ly() gets the aspect ratio wrong if using the shapefile-based set of multipolygons that I used with ggplot() and ggplotly() maps. I'm not sure why.

Also, the shapefiles are probably higher resolution than needed. Using the lower res geojson polygons saves nearly 3mb on the total file size.

# Leaflet

## Column {data-width=750}

### **Leaflet** 

`r paste("<p style='font-size:20px; font-family:sans-serif; font-weight:bold '>10 Day Average Covid-19 Test Positivity<br>in Connecticut Towns<br>for period ending", format(max(ct.covid$Date), "%B %d, %Y"), "</p>") `

```{r leaflet}

map.positivity.leaflet

```

## Column {data-width=250}

### **Notes**

Interactive choropleth via leaflet::leaflet(). 

Previous plots in this series used multipolygon shapes for towns taken from conventional shape files. I couldn't get that to work with leaflet and so switched to simple polygons. These were read from geojson files, but I think the crucial difference is multipolygon vs. somple polygons. 

I don't know why the colorscale in the legend is inverted relative to expectations. It's annoying, but there doesn't seem to be a way to correct it. A couple of "solutions" I've seen proposed on StackOverflow just don't work. 

Leaflet maps don't provide a "title" feature, as such. Here, I've just added the title text above the map. Formatting is by way of the `<font>` tag. It's not best practice, but it works.

# About

## Column {data-width=333}

### About the Maps

Covid data for these figures was compiled by CT Dept. of Public Health through `r format(max(ct.covid$Date), "%b %d, %Y")` and accessed through https://data.ct.gov/stories/s/COVID-19-data/wa3g-tfvc/#data-library.

Figures were created by David Braze (davebraze@gmail.com) using R statistical software and released under the Creative Commons v4.0 CC-by license.

You can always find the most current version of this data sketch online at: https://davebraze.github.io/ct-covid-map-examples/ . 

## Column {data-width=333}

### About the Author

David Braze is a researcher and consultant with a background in linguistics and reading research. He has more than 25 years experience investigating the cognitive foundations of language, literacy, and educational achievement, including 17 years as a Senior Research Scientist at [Haskins Laboratories](https://haskinslabs.org/). His research at Haskins, funded by the National Institutes of Health, emphasized the neurobiology of language and reading and applications to education. Dr. Braze consults widely for business, government, and non-profit sectors. 

|   email: davebraze@gmail.com
|   website: [davebraze.org](https://davebraze.org/ "D. Braze's website")


## Column {data-width=333}

### About the Software

All data summaries in this dashboard were produced with the _R_ statistical environment, version `r paste(version$major, version$minor, sep=".")`. The dashboard itself was made using an Rmarkdown workflow. The following table lists the non-base R packages used in building the dashboard. To see a full citation for a specific package, assuming you have both _R_ and the particular package installed, call (e.g.) `citation("dplyr")` from the _R_ prompt. 

```{r r-package-tab, include=TRUE}

package_tab <-
    sessioninfo::package_info() %>%
    unclass() %>%
    as_tibble() %>%
    filter(attached == TRUE) %>%
    select(package, ondiskversion, date) %>%
    rename(version = ondiskversion)
caption <- "R packages used in this dashboard."
package_tab %>%
    FDBpub::format_table(caption=caption, out_type=doc_type())

```
